\chapter{Generalised Motion Groups}
\label{chapter:generalised_motion_groups}

\section{Definitions}
\label{section:definitions}

\begin{definition}[semi-direct product]
\label{definition:semi-direct_products}
\index{semi-direct product}
    Let $N$ be a group and $H$ be a subgroup of $\Aut(N)$.
    The \emph{semi-direct product} $N \rtimes H$ is the group whose elements are that of $N \times H$ with the group law:
    \begin{align}
        (n_1, h_1) (n_2, h_2) = (n_1 h_1(n_2), h_1 h_2), \quad (n_1, h_1), (n_2, h_2) \in N \times H.
    \end{align}

    Given $(n, h)$ in $N \rtimes H$, its \emph{inverse} is given by $({h_1}^{-1}({n_1}^{-1}), {h_1}^{-1})$,
    while $(e_N, e_H)$ is the \emph{identity element} of the group.
\end{definition}

\begin{definition}[generalised motion group]
\label{definition:generalised_motion_group}
\index{generalised motion group}
    Let $\Group$ be a group.
    We shall say that $\Group$ is a \emph{generalised motion group}
    if there exists a vector space $\VectorSpace$ and a compact group $\CompactGroup \subset \Aut(\VectorSpace)$ such that $\Group = \VectorSpace \rtimes \CompactGroup$.
\end{definition}

From now on, unless stated otherwise,
$\Group$ will denote a generalised motion group,
with $\VectorSpace$ its underlying vector space and $\CompactGroup$ its associated compact group.

\section{Unitary representations}
\label{section:unitary_representations}

\begin{definition}
\label{definition:reducible_representation}
    Let $\rho \in \dualGroup{V}$.
    We define a unitary representation $\Rep{\rho} \in \Hom(\Group, \End(\Lebesgue{2}{\CompactGroup}))$ of $\Group$ via:
    \begin{align}
        \Rep{\rho} (x, k) F(u) = \rho(u^{-1} x) F(k^{-1} u),
    \end{align}
    where $(x, k) \in \CompactGroup$, $F \in \Lebesgue{2}{\CompactGroup}$ and $u \in \CompactGroup$.
\end{definition}

The above representation is unfortunately reducible.
However, as we shall see later, the Fourier Transform on $\Group$ can be written exclusively with those representations.

\subsection{Unitary dual}
\label{subsection:unitary_dual}

Throughout this section, fix $\rho \in \dualGroup{V}$
and denote by $\IsotropySubgroup{\CompactGroup}{\rho}$ its isotropy subgroup.

Let $\sigma \in \dualGroup{\IsotropySubgroup{\CompactGroup}{\rho}}$ and denote by $\dimRep{\sigma}$ its dimension.
For $q = 1, \dots, \dimRep{\sigma}$, let:
\begin{align}
    P^\sigma_q F(u) = \dimRep{\sigma} \int_\IsotropySubgroup{\CompactGroup}{\rho} \conj{\sigma_{qq}(m)} F(u m) \dd m,
    \quad F \in \Lebesgue{2}{\CompactGroup}.
\end{align}

By the Inverse Fourier Transform at $e \in \IsotropySubgroup{\CompactGroup}{\rho}$,
if $F \in \Lebesgue{2}{\CompactGroup}$ and $u \in \CompactGroup$, then:
\begin{align}
    F(u)
    = \sum_{\sigma \in \dualGroup{\IsotropySubgroup{\CompactGroup}{\rho}}} \dimRep{\sigma} \sum_{q = 1}^{\dimRep{\sigma}} {\Fourier[\IsotropySubgroup{\CompactGroup}{\rho}]{F(u \dummy)}}_{qq}
    = \sum_{\sigma \in \dualGroup{\IsotropySubgroup{\CompactGroup}{\rho}}} P^\sigma_q F(u)
\end{align}

Now, write $\Hilbert{\sigma}{q} = P^\sigma_q \Lebesgue{2}{\CompactGroup}$.

\begin{lemma}
    The Hilbert spaces
    \begin{align*}
        \{\Hilbert{\sigma}{q} : \sigma \in \dualGroup{\IsotropySubgroup{\CompactGroup}{\rho}}, q = 1, \dots, \dimRep{\sigma} \}
    \end{align*}
    are mutually orthogonal.
    Therefore, we have
    \begin{align*}
        \Lebesgue{2}{K} = \bigoplus_{\sigma \in \dualGroup{\IsotropySubgroup{\CompactGroup}{\rho}}} \bigoplus_{q = 1}^{\dimRep{\sigma}} \Hilbert{\sigma}{q},
    \end{align*}
    where the above decomposition is orthogonal.
\end{lemma}

\begin{proposition}[Unitary dual]
\label{proposition:unitary_dual}
    Let $\rho, \rho' \in \dualGroup{\VectorSpace}$
    and $\sigma \in \dualGroup{\IsotropySubgroup{\CompactGroup}{\rho}}$,
    $\sigma' \in \dualGroup{\IsotropySubgroup{\CompactGroup}{\rho'}}$.
    The following properties hold:
    \begin{enumerate}
        \item $\Rep{\rho}$ restricts to an irreducible unitary representation on each $\Hilbert{\sigma}{q}$;
        \item $(\Hilbert{\sigma}{q}, \Rep{\rho})$ and $(\Hilbert{\sigma'}{q'}, \Rep{\rho'})$ are equivalent if and only if
            \begin{align*}
                \rho' = k \rho \quad \text{and} \quad \EquivalenceClass{\dualGroup{\IsotropySubgroup{\CompactGroup}{\rho}}}{\sigma} = \EquivalenceClass{\dualGroup{\IsotropySubgroup{\CompactGroup}{\rho}}}{\sigma'(k \dummy k^{-1})}
            \end{align*}
            for some $k \in \CompactGroup$.
    \end{enumerate}
\end{proposition}

\section{Fourier Transform}
\label{section:Fourier_transform}

\begin{definition}[Fourier transform]
\label{definition:Fourier_Transform}
\index{Fourier transform}
    Let $f \in \Lebesgue{1}{\Group}$ and $\rho \in \dualGroup{\VectorSpace}$.
    We define its \emph{Fourier coefficient} at $\rho$ via:
    \begin{align*}
        \Fourier{f}(\rho) = \int_\Group f(g) \adj{\Rep{\rho}(g)} \dd g.
    \end{align*}

    Moreover, the map
    \begin{align*}
        \Fourier{f} : \dualGroup{V} \to \End(\Lebesgue{2}{\CompactGroup}) :
        \rho \mapsto \Fourier{f}(\rho)
    \end{align*}
    is called the \emph{Fourier Transform} of $f$.
\end{definition}

\begin{proposition}[Plancherel formula]
\label{proposition:Plancherel_formula}
\index{Plancherel formula}
    Let $f \in \Lebesgue{1}{\Group} \cap \Lebesgue{2}{\Group}$.
    The following formula holds:
    \begin{align}
        \int_G \abs{f}^2 \dd g = \int_\dualGroup{\VectorSpace} \norm[\HilbertSchmidt{\Lebesgue{2}{\CompactGroup}}]{\Fourier{f}(\rho)}^2 \dd \Plancherel{\VectorSpace}(\rho).
        \label{proposition:Plancherel_formula:formula}
    \end{align}
\end{proposition}
\begin{proof}
    Let $\rho \in \dualGroup{\VectorSpace}$ and $F \in \Lebesgue{2}{\CompactGroup}$.
    If $u \in \CompactGroup$, we can check that
    \begin{align*}
        \Fourier{f}(\rho) F(u)
        &= \int_\VectorSpace \int_\CompactGroup f(x, k) \rho(-u^{-1} k^{-1} x) F(k u) \dd k \dd x\\
        &= \int_\VectorSpace \int_\CompactGroup f(x, k) \conj{k u \rho(x)} F(k u) \dd k \dd x,
    \end{align*}
    where we used $\rho(-{(k u)}^{-1} x) = \conj{\rho({(k u)}^{-1} x)} = \conj{(k u \rho)(x)}$.

    Substituing $k$ for $k u^{-1}$, we get:
    \begin{align*}
        \Fourier{f}(\rho) F(u)
        &= \int_\CompactGroup \Fourier[\VectorSpace]{f}(k \rho, k u^{-1}) F(k) \dd k.
    \end{align*}

    Therefore, it follows by REFERENCE that:
    \begin{align*}
        \norm[\HilbertSchmidt{\Lebesgue{2}{\CompactGroup}}]{\Fourier{f}(\rho)}^2
        &= \int_\CompactGroup \int_\CompactGroup \abs{\Fourier[\VectorSpace]{f}(k \rho, k u^{-1})}^2 \dd u \dd k.
    \end{align*}

    Now, integrating with respect to $\rho$, we obtain:
    \begin{align*}
        \int_\dualGroup{\VectorSpace} \norm[\HilbertSchmidt{\Lebesgue{2}{\CompactGroup}}]{\Fourier{f}(\rho)}^2 \dd \Plancherel{\VectorSpace}(\rho)
        &= \int_\dualGroup{\VectorSpace} \int_\CompactGroup \abs{\Fourier[\VectorSpace]{f}(\rho, k)}^2 \dd k \dd \Plancherel{\VectorSpace}(\rho)\\
        &= \int_\VectorSpace \int_\CompactGroup \abs{f(x, k)}^2 \dd u \dd k,
    \end{align*}
    where the last line was obtained by applying the Plancherel formula on $\VectorSpace$.
\end{proof}
